---
title: "Assignment 14"
author: "Tyler Baker"
date: "5/1/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pracma)
```

# Assignment 14
## Tyler Baker

This week, we’ll work out some Taylor Series expansions of popular functions.

For each function, only consider its valid ranges as indicated in the notes when you are
computing the Taylor Series expansion. Please submit your assignment as a R-Markdown
document.

### Question 1:
$f(x)=1/(1-x)$
We first need to make note that $|x|<1$ for the series to converge.

$f(x) = \sum_{n=0}^{inf} (f^na)/n!(x-a)^n$
$f(a) + f^1(a)(x-a) + (f^2)/2!(a)(x-a) + ...$

The derivatives are:
$f(a) = 1/(1-a)$
$f'(a) = 1/(1-a)^2$
$f''(a) = 2/(1-a)^3$

so we get
$ = 1 + x + x^2 + x^3  + ...$
$\sum_{n=0}^{inf} x^n$

```{r}
f <- function(x){1/(1-x)}
taylor(f, x0=0, n=4)
```
### Question 2
The Taylor expansion will converge for all x.
$f(x) = e^x$
$f(x) = \sum_{n=0}^{inf} (f^na)/n!(x-a)^n$

The derivatives are 
$f(a) = e^a$
$f'(a) = e^a$
$f''(a) = e^a$
$f'''(a)= e^a$
and so on.

So we get
$S = 1 + x +  x^2/2! +  x^3/3! +...$
$\sum_{n=0}^{inf} x^n/n!$
```{r}
f <- function(x){exp(x)}
taylor(f, x0=0, n=4)
```

### Question 3
$f(x)=ln(1+x)$
The series will converge for $x \in (-1,1]$.

The derivatives are
$f(a) = ln(1+a)$
$f'(a) = 1/(1+a)$
$f''(a) = -1/(x+1)^2$
$f'''(a) = 2/(x+1)^3$

So we get
$S = x - x^2/2 + x^3/3 - x^4/4 +...$
$S = \sum_{n=0}^{inf} (-1)^(n+1) *x^n/n$
```{r}
taylor(f, x0=0, n=4)
```

### Question 4
$f(x)=x^(1/2)$
$f(x)=sqrt(x)$

There is no Taylor Series Expansion for $f(x)$ because it will blow up when we evaluate the first the derivative at $x=0$.